\ttitle

### 2015-07-08 Chapters/CRP_Complications.tex
CRP Complications - ROC Analysis - Infective complications
- Create d3-7 ROC figures
- Create 2 new tables - crp vs. infections, ROC
- Modify chapter to include above

%==============================================================================
%CRP trends in a 2-panel figure and table showing p-values below it
\clearpage
\begin{figure}[htbp]
	\centering
	\begin{subfigure}{0.45\textwidth}
		\centering
		\includegraphics[width=\textwidth]{Figures/crp_comp_crp_popf_yes_no}
		\caption{POPF Absent vs. Any Grade}
		\label{fig:crp_comp_crp_popf_yes_no}
	\end{subfigure}
	\begin{subfigure}{0.45\textwidth}
		\centering
		\includegraphics[width=\textwidth]{Figures/crp_comp_crp_popf_isgps}
		\caption{POPF ISGPS Grades}
		\label{fig:crp_comp_crp_popf_isgps}
	\end{subfigure}

@@

%==============================================================================
%CRP trends in a 2-panel figure and table showing p-values below it
\clearpage
\begin{figure}[htbp]
	\centering
	\begin{subfigure}{0.45\textwidth}
		\centering
		\includegraphics[width=\textwidth]{Figures/crp_comp_infectious_leak0}
		\caption{Patients with \textbf{\underline{no}} POPF}
		\label{fig:crp_comp_infectious_leak0}
	\end{subfigure}
	\begin{subfigure}{0.45\textwidth}
		\centering
		\includegraphics[width=\textwidth]{Figures/crp_comp_infectious_leak1}
		\caption{Patients with POPF}
		\label{fig:crp_comp_infectious_leak1}
	\end{subfigure}

@@

>>>>

%========================CRP vs POPF============================================
%CRP trends in a 2-panel figure and table showing p-values below it
\clearpage
\begin{figure}[htbp]
	\centering
	\begin{subfigure}{0.45\textwidth}
		\centering
		\includegraphics[width=\textwidth]{Figures/crp_comp_crp_popf_yes_no}
		\caption{POPF Absent vs. Any Grade}
		\label{fig:crp_comp_crp_popf_yes_no}
	\end{subfigure}
	\begin{subfigure}{0.45\textwidth}
		\centering
		\includegraphics[width=\textwidth]{Figures/crp_comp_crp_popf_isgps}
		\caption{POPF ISGPS Grades}
		\label{fig:crp_comp_crp_popf_isgps}
	\end{subfigure}

@@

%========================CRP vs Infections====================================
%CRP trends vs infections in patients with or without popf in a 2-panel figure and table showing median, iqr and p-values below it
\clearpage
\begin{figure}[t]
	\centering
	\begin{subfigure}{0.45\textwidth}
		\centering
		\includegraphics[width=\textwidth]{Figures/crp_comp_infectious_leak0}
		\caption{Patients with \textbf{\underline{no}} POPF}
		\label{fig:crp_comp_infectious_leak0}
	\end{subfigure}
	\begin{subfigure}{0.45\textwidth}
		\centering
		\includegraphics[width=\textwidth]{Figures/crp_comp_infectious_leak1}
		\caption{Patients with POPF}
		\label{fig:crp_comp_infectious_leak1}
	\end{subfigure}

@@

%========================ROC Curves==========================================
\clearpage
\begin{figure}[t]
	\centering
	\begin{subfigure}{0.3\textwidth}
		\centering
		\includegraphics[width=\textwidth]{Figures/crp_comp_ROC_infection_D3}
		\caption{Day 3}
		\label{fig:crp_comp_ROC_infection_D3}
	\end{subfigure}
	\begin{subfigure}{0.3\textwidth}
		\centering
		\includegraphics[width=\textwidth]{Figures/crp_comp_ROC_infection_D4}
		\caption{Day 4}
		\label{fig:crp_comp_ROC_infection_D4}
	\end{subfigure}
	\begin{subfigure}{0.3\textwidth}
		\centering
		\includegraphics[width=\textwidth]{Figures/crp_comp_ROC_infection_D5}
		\caption{Day 5}
		\label{fig:crp_comp_ROC_infection_D5}
	\end{subfigure}
	\begin{subfigure}{0.3\textwidth}
		\centering
		\includegraphics[width=\textwidth]{Figures/crp_comp_ROC_infection_D6}
		\caption{Day 6}		
		\label{fig:crp_comp_ROC_infection_D6}
	\end{subfigure}
	\begin{subfigure}{0.3\textwidth}
		\centering
		\includegraphics[width=\textwidth]{Figures/crp_comp_ROC_infection_D7}
		\caption{Day 7}
		\label{fig:crp_comp_ROC_infection_D7}
	\end{subfigure}

	\caption{Receiver operating characteristics curve analysis of C-reactive protein as a marker of postoperative infective complications.}
	\label{fig:crp_comp_ROC_infection}

\end{figure}
\input{Tables/crp_comp_ROC_infections_noPOPF}
